### 2023-04-04 chapter2/chapter2_supporting.tex
Added citation link to table header

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|l|l|l|l|}
\caption{\textbf{Features and their definitions.}}
\label{stable:features}
% Start first head
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Source} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}\end{tabular}
\endfirsthead

% Start head
\multicolumn{6}{l}
{\textbf{\tablename\ \thetable} (continued)} \\
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Source} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}\end{tabular}
\endhead

>>>>

\begin{landscape}
\footnotesize
\begin{longtable}{|l|l|l|l|l|l|}
\caption{\textbf{Features and their definitions.}}
\label{stable:features}
% Start first head
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Source} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}}~\cite{Zarin2019}\end{tabular}
\endfirsthead

% Start head
\multicolumn{6}{l}
{\textbf{\tablename\ \thetable} (continued)} \\
\hline
\textbf{Feature ID}    & \textbf{Feature name}                                                            & \textbf{Group name}                                                & \textbf{Source} & \textbf{Description}                                                                                                             & \begin{tabular}[c]{@{}l@{}}\textbf{Changes from}\\\textbf{Zarin \textit{et al.}~\cite{Zarin2019}}\end{tabular}
\endhead
